A Critical Review of Sophistication and Model Selection in Algorithmic Statistics

### 2014-12-08 Facticity/Facticity/paper.tex
...

>>>>

\begin{lemma}
Let $f$ be a total, computable function, such that for some $d$, $f(d) = x$ and let $k = K(f) + |d|$. Then there exists a finite set $S$ containing $x$, such that we have $K(S) \leq K(f) + K(|d|)$ and $\log |S| \leq |d|$.\label{lemma:total-to-sets}
\end{lemma}
\begin{proof}
Let $S = \{f(y) : |y| = |d|\}$. Since $f$ is total, this set can be explicity computed from a description of $f$ and a description of $|d|$, this tells us that there is a constant such that $K(S) \leq K(f) + K(|d|) + c$.

Note that the inputs $y$ used to construct all have length $|d|$, so that $S$ contains at most $2^{|d|}$ strings. Therefore, we have $\log |S| \leq |d|$.
\end{proof}
This lemma is an extension of \cite[Lemma~7.2]{vitanyi2004meaningful} and uses approximately the same proof.

\begin{theorem}
There are $x$, such that $S^\T(x) \geq \tfrac{1}{4}K(x)$.
\end{theorem}
\begin{proof}
Let $x\geq n$ be ($\tfrac{1}{4n}$, $\tfrac{1}{4}$)-stochastic. This means that for any $S$ containing $x$ with $K(S) \leq \tfrac{1}{4}$ we have $K(S) + \log|S| \geq K(x) + \tfrac{3}{4}n$. \ldots
\end{proof}
